---
title: "Reproduce p-values in letter"
author: "Dominic Magirr"
date: "5/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Figure 1 (A)

### Data

The data in Figure 1 (A) were extracted manually from 

Mok, Tony SK, et al. "Pembrolizumab versus chemotherapy for previously untreated, PD-L1-expressing, locally advanced or metastatic non-small-cell lung cancer (KEYNOTE-042): a randomised, open-label, controlled, phase 3 trial." The Lancet 393.10183 (2019): 1819-1830.

using the same techniques as described in Friedlin \& Korn.

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
library(survival)
#########################
## start here
df_mok <- rbind(read.csv("mok_3c_control_ipd.csv")[,-1],
                read.csv("mok_3c_pembro_ipd.csv")[,-1])
head(df_mok)
```

### KM plot

```{r}
df_mok$trt <- ifelse(df_mok$arm == 1, "Pembrolizumab", "Chemotherapy")
KM.est<-survfit(Surv(time,event)~arm, data=df_mok, type="kaplan-meier")
p1 <- survminer::ggsurvplot(KM.est, 
                            data = df_mok, 
                            risk.table = TRUE, 
                            break.x.by = 6,
                            legend.labs = c("control", "test"),
                            legend.title = "",
                            xlab = "Time (months)",
                            ylab = "Progression-free survival",
                            risk.table.fontsize = 4,
                            title = "                        (A)",
                            legend = c(0.8,0.8))

p1
```

### P-values


```{r}
### get survival probabilities for the pooled data
s_pool <- summary(survfit(Surv(time,event)~1, data= df_mok))$surv

### standard log-rank test weights
w_lr <- rep(1, length(s_pool))

### Fleming-Harrington (0,1) test weights
w_fh <- 1 - c(1, s_pool[-length(s_pool)])

### modest weights
w_mw <- pmin(1 / c(1, s_pool[-length(s_pool)]), 2)

### produce risk table
rt_row <- function(t_star, df){
  
  df1 = df[df$arm == unique(df$arm)[1],]
  df2 = df[df$arm == unique(df$arm)[2],]
  data.frame(time = t_star,
             r1 = sum(df1$time >= t_star),
             r2 = sum(df2$time >= t_star),
             e1 = sum(df1$time == t_star & df1$event == 1),
             e2 = sum(df2$time == t_star & df2$event == 1))
}

rt <- purrr::map_df(unique(df_mok$time), 
                    rt_row, 
                    df = df_mok) %>% 
  arrange(time) %>% 
  filter(e1 > 0 | e2 > 0)

### produce p-values
p_wlrt <- function(rt, w){
  
  u = sum(w * (rt$e2 - (rt$e1+rt$e2) * rt$r2 / (rt$r1+rt$r2)))
  v_u = sum(w^2 * rt$r1 * rt$r2 * (rt$e1+rt$e2) * (rt$r1+rt$r2 - (rt$e1+rt$e2)) / ((rt$r1+rt$r2)^2 * (rt$r1+rt$r2-1)), na.rm = TRUE)
  
  
  z = u / sqrt(v_u)
  pnorm(z)
}


p_wlrt(rt, w = w_lr)
p_wlrt(rt, w = w_fh)
p_wlrt(rt, w = w_mw)

```

## Figure 1 (B)

### Data

The data in Figure 1 B were generated using the prescription in Friedlin \& Korn:

```{r}
set.seed(102)
t_c <- rexp(n = 1000, rate = 0.25)

t_e_1 <- rexp(n = 1000, rate = 4)
t_e_2 <- rexp(n = 1000, rate = 0.19)
t_e <- ifelse(t_e_1 < 0.1, t_e_1, 0.1 + t_e_2)

event_c = t_c < 5
event_e = t_e < 5
time_c = pmin(t_c, 5)
time_e = pmin(t_e, 5)


df_B <- data.frame(time = c(time_c, time_e),
                   event = c(event_c, event_e),
                   arm = rep(c("C", "E"), c(1000, 1000)))
```


### KM plot

```{r}
fit_B <- survfit(Surv(time, event)~arm, data = df_B)

p2 <- survminer::ggsurvplot(fit_B, 
                            data = df_B, 
                            risk.table = TRUE, 
                            break.x.by = 1,
                            legend.labs = c("control", "test"),
                            legend.title = "",
                            ylab = "Overall survival",
                            xlab = "Time (years)",
                            risk.table.fontsize = 4,
                            title = "                        (B)",
                            legend = c(0.8,0.8))

p2

#survminer::arrange_ggsurvplots(list(p1, p2))
```



### P-values



```{r}
s_pool <- summary(survfit(Surv(time,event)~1, data= df_B))$surv
w_lr <- rep(1, length(s_pool))
w_fh <- 1 - c(1, s_pool[-length(s_pool)])
w_mw <- pmin(1 / c(1, s_pool[-length(s_pool)]), 2)
rt <- purrr::map_df(unique(df_B$time), 
                    rt_row, 
                    df = df_B) %>% 
  arrange(time) %>% 
  filter(e1 > 0 | e2 > 0)
p_wlrt(rt, w = w_lr)
p_wlrt(rt, w = w_fh)
p_wlrt(rt, w = w_mw)
```

